Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-17 paper.tex
minor sentence fix

        \note{pipeline description}
        A pipeline in PSOM, is a series of connected jobs, which can be
represented as a directed acyclic graph. The pipeline itself is implemented 
using the Matlab/Octave data type. Each job within the pipeline
is assigned a unique name. There is only one mandatory field in the job
description (command). The remaining four optional fields include the list input
files (files_in), the list output files (files_out), the list of files to be
deleted after execution (files_clean) and any Octave or Matlab datatype
containing any remaining optional parameters necessary for job execution (opt).
Jobs in PSOM run in a protected environment where they only have access to the
parameters that are passed.

>>>>

        \note{pipeline description}
        A pipeline in PSOM, is a series of connected jobs, which can be
represented as a directed acyclic graph. The pipeline itself is implemented 
using the Matlab/Octave data type. Each job within the pipeline
is assigned a unique name. There is only one mandatory field in the job
description (command). The remaining four optional fields include the list input
files (files_in), the list output files (files_out), the list of files to be
deleted after execution (files_clean) and any Octave or Matlab datatype
containing the remaining parameters necessary for job execution (opt).
Jobs in PSOM run in a protected environment where they only have access to the
parameters that are passed.
